Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-18 sections/pitfalls.tex
minor changes, added acknowledgements
Update pitfalls.tex
First typo-correction

In the case of combining SICM with a scanning technique such as STED, there
are two alignment options: The first one is aligning the pipette tip and the
laser beam only in the $x,y$ plane. This is comparable, in terms of data
recording, to the above mentioned combinations of SICM and wide-field or
confocal microscopy.  The second one, surface scanning, requires the
additional alignment of the tip and, in case of STED, the two beams in the
$z$-plane.

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:

>>>>

In the case of combining SICM with a scanning technique such as STED, there
are two alignment options: The first one is aligning the pipette tip and the
laser beam only in the $x,y$-plane. This is comparable, in terms of data
recording, to the above mentioned combinations of SICM and wide-field or
confocal microscopy. The second one, surface scanning, requires the
additional alignment of the tip and, in case of STED, the two beams in the
$z$-plane.

@@

\section{Acknowledgements}
The authors acknowledge support from the Volkswagen
Foundation (grant 88 390) and the German Research Foundation (grant
411517989). 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
